Tablas_Ms_ HabitatAves

### 2020-10-16 Tablas_Ms_HabitatAves.Rmd
Ocupancia especifica para especies obtenidas de simper, guardado de datos y nuevo .Rmd con tablas de manuscrito

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus_thagus", "Phalacrocorax_bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23 \\times native forest - 21.04 \\times gravel + 44.82 \\times sand}$", "$\\psi_{Cl} = e^{12.45}$", "$\\psi_{Cl} = e^{	47.82 -5.09 \\times altitude -231.04 \\times gravel + 5.74 \\times ocean + 	4.40 \\times paved surface}$", "$\\psi_{Cl} = e^{104.91 -0.59 \\times altitude +	6.56\\times native forest 	-2.93 \\times shrublands -18.98\\times sand}$", "$\\psi_{Cl} = e^{-82.05 + 	12.46 \\times crops -15.13 \\times gravel + 	1.38 \\times ocean}$"))

kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")

@@

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus_thagus", "Phalacrocorax_bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23 \\times native forest - 21.04 \\times gravel + 44.82 \\times sand}$", "$\\psi_{Cl} = e^{12.45}$", "$\\psi_{Cl} = e^{	47.82 -5.09 \\times altitude -231.04 \\times gravel + 5.74 \\times ocean + 	4.40 \\times paved surface}$", "$\\psi_{Cl} = e^{104.91 -0.59 \\times altitude +	6.56\\times native forest 	-2.93 \\times shrublands -18.98\\times sand}$", "$\\psi_{Cl} = e^{-82.05 + 	12.46 \\times crops -15.13 \\times gravel + 	1.38 \\times ocean}$"))

kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")

>>>>

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23Na - 21.04Gr + 44.82Sa}$",
                               "$\\psi_{Ld} = e^{12.45}$", 
                               "$\\psi_{Lp} = e^{47.82 -5.09Al -231.04Gr + 5.74Oc + 	4.40Pa}$", 
                               "$\\psi_{Pt} = e^{104.91 -0.59Al +	6.56Na	-2.93Sh -18.98Sa}$", 
                               "$\\psi_{Pb} = e^{-82.05 + 12.46Cr -15.13Gr + 	1.38Oc}$"))

kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)

@@

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia","Coragyps atratus", "Larosterna inca", "Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Sephanoides sephaniodes", "Turdus falcklandii"), 
                   Equation= c("$\\psi_{Cl} = e^{-1.77 + 1.83Sa}$", 
                               "$\\psi_{Ca} = e^{7.57 -3.29Pa +	33.80Sa}$", 
                               "$\\psi_{Li} = e^{140.42 -2.38Al	-92.31Na -38.88Sa}$", 
                               "$\\psi_{Ld} = e^{2289.33}$",
                               "$\\psi_{Lm} = e^{190.57 + 2.73Ve -4.07Al -134.07Gr +	20.05Sa}$", 
                               "$\\psi_{Pt} = e^{172.98 -2.01Al	-50.93Na -165.09Gr +	2.47Oc}$", 
                               "$\\psi_{Ss} = e^{-106.91 + 1.64Ve +	7.14Al -43.91Na +	5.09Sh -24.45Tr}$", 
                               "$\\psi_{Tf} = e^{687.42 + 29.20Ve +	48.41Al -34.88Oc	-505.66Gs +	59.49Tr -4.94Pa +	283.63Sa -51.82Tr}$"))

kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
#dear silvain
```
